---
title: "Laboratorio 1 An치lisis Exploratorio"
author: "Marco Ramirez 19588, Estuardo Hernandez 19202"
date: '2022-07-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# An치lisis Exploratorio

```{r include= FALSE}



db<-read.csv('train.csv')
```

## Resumen de datos

```{r}
summary(db)
```

## Tipos de variables

#### Id: Cuantitativa discreta
#### MSSubClass: Cuantitativa discreta
#### MSZoning: Cualitativa
#### LotFrontage: Cuantitativa continua
#### LotArea: Cuantitativa continua
#### Street: Cualitativa
#### Alley: Cualitativa
#### LotShape: Cualitativa
#### LandContour: Cualitativa
#### Utilities: Cualitativa
#### LotConfig: Cualitativa
#### LandSlope: Cualitativa
#### Neighborhood: Cualitativa
#### Condition1: Cualitativa
#### Condition2: Cualitativa
#### BldgType: Cualitativa
#### HouseStyle: Cualitativa
#### OverallQual: Cuantitativa discreta
#### OverallCond: Cuantitativa discreta
#### YearBuilt: Cuantitativa discreta
#### YearRemodAdd: Cuantitativa discreta
#### RoofStyle: Cualitativa
#### RoofMatl: Cualitativa
#### Exterior1st: Cualitativa
#### Exterior2nd: Cualitativa
#### MasVnrType: Cualitativa
#### MasVnrArea: Cuantitativa continua
#### ExterQual: Cualitativa
#### ExterCond: Cualitativa
#### Foundation: Cualitativa
#### BsmtQual: Cualitativa
#### BsmtCond: Cualitativa
#### BsmtExposure: Cualitativa
#### BsmtFinType1: Cualitativa
#### BsmtFinSF1: Cuantitativa continua
#### BsmtFinType2: Cualitativa
#### BsmtFinSF2: Cuantitativa continua
#### BsmtUnfSF: Cuantitativa continua
#### TotalBsmtSF: Cuantitativa continua
#### Heating: Cualitativa
#### HeatingQC: Cualitativa
#### CentralAir: Cualitativa
#### Electrical: Cualitativa
#### X1stFlrSF: Cuantitativa continua
#### X2ndFlrSF: Cuantitativa continua
#### LowQualFinSF: Cuantitativa continua
#### GrLivArea: Cuantitativa continua
#### BsmtFullBath: Cuantitativa discreta
#### BsmtHalfBath: Cuantitativa discreta
#### FullBath: Cuantitativa discreta
#### HalfBath: Cuantitativa discreta
#### BedroomAbvGr: Cuantitativa discreta
#### KitchenAbvGr: Cuantitativa discreta
#### KitchenQual: Cualitativa
#### TotRmsAbvGrd: Cuantitativa discreta
#### Functional: Cualitativa
#### Fireplaces: Cuantitativa discreta
#### FireplaceQu: Cualitativa
#### GarageType: Cualitativa
#### GarageYrBlt: Cuantitativa discreta
#### GarageFinish: Cualitativa
#### GarageCars: Cuantitativa discreta
#### GarageArea: Cuantitativa continua
#### GarageQual: Cualitativa
#### GarageCond: Cualitativa
#### PavedDrive: Cualitativa
#### WoodDeckSF: Cuantitativa continua
#### OpenPorchSF: Cuantitativa continua
#### EnclosedPorch: Cuantitativa continua
#### x3SsnPorch: Cuantitativa discreta
#### ScreenPorch: Cuantitativa continua
#### PoolArea: Cuantitativa continua
#### PoolQC: Cualitativa
#### Fence: Cualitativa
#### MiscFeature: Cualitativa
#### MiscVal: Cuantitativa continua
#### MoSold: Cuantitativa discreta
#### YrSold: Cuantitativa discreta
#### SaleType: Cualitativa
#### SaleCondition: Cualitativa

## Representaci칩n gr치fica
### Continuas

```{r}
hist(x = db$LotFrontage)
hist(x = db$LotArea)
hist(x = db$MasVnrArea)
hist(x = db$BsmtFinSF1)
hist(x = db$BsmtFinSF2)
hist(x = db$BsmtUnfSF)
hist(x = db$TotalBsmtSF)
hist(x = db$X1stFlrSF)
hist(x = db$X2ndFlrSF)
hist(x = db$LowQualFinSF)
hist(x = db$GrLivArea)
hist(x = db$GarageArea)
hist(x = db$WoodDeckSF)
hist(x = db$OpenPorchSF)
hist(x = db$EnclosedPorch)
hist(x = db$ScreenPorch)
hist(x = db$PoolArea)
hist(x = db$MiscVal)
```

### Discretas

```{r}

```

### Cualitativas

```{r}

```
