---
title: "Laboratorio 1 An치lisis Exploratorio"
author: "Marco Ramirez 19588, Estuardo Hernandez 19202"
date: '2022-07-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# An치lisis Exploratorio

```{r include= FALSE}
db<-read.csv('train.csv')

t1<-table(db$MSZoning)
t2<-table(db$Street)
t3<-table(db$Alley)
t4<-table(db$LotShape)
t5<-table(db$LandContour)
t6<-table(db$Utilities)
t7<-table(db$LotConfig)
t8<-table(db$LandSlope)
t9<-table(db$Neighborhood)
t10<-table(db$Condition1)
t11<-table(db$Condition2)
t12<-table(db$BldgType)
t13<-table(db$HouseStyle)
t14<-table(db$RoofStyle)
t15<-table(db$RoofMatl)
t16<-table(db$Exterior1st)
t17<-table(db$Exterior2nd)
t18<-table(db$MasVnrType)
t19<-table(db$ExterQual)
t20<-table(db$ExterCond)
t21<-table(db$Foundation)
t22<-table(db$BsmtQual)
t23<-table(db$BsmtCond)
t24<-table(db$BsmtExposure)
t25<-table(db$BsmtFinType1)
t26<-table(db$BsmtFinType2)
t27<-table(db$Heating)
t28<-table(db$HeatingQC)
t29<-table(db$CentralAir)
t30<-table(db$Electrical)
t31<-table(db$KitchenQual)
t32<-table(db$Functional)
t33<-table(db$FireplaceQu)
t34<-table(db$GarageType)
t35<-table(db$GarageFinish)
t36<-table(db$GarageQual)
t37<-table(db$GarageCond)
t38<-table(db$PavedDrive)
t39<-table(db$PoolQC)
t40<-table(db$Fence)
t41<-table(db$MiscFeature)
t42<-table(db$SaleType)
t43<-table(db$SaleCondition)
```

## Resumen de datos

```{r}
summary(db)
```

## Tipos de variables

#### Id: Cuantitativa discreta
#### MSSubClass: Cuantitativa discreta
#### MSZoning: Cualitativa
#### LotFrontage: Cuantitativa continua
#### LotArea: Cuantitativa continua
#### Street: Cualitativa
#### Alley: Cualitativa
#### LotShape: Cualitativa
#### LandContour: Cualitativa
#### Utilities: Cualitativa
#### LotConfig: Cualitativa
#### LandSlope: Cualitativa
#### Neighborhood: Cualitativa
#### Condition1: Cualitativa
#### Condition2: Cualitativa
#### BldgType: Cualitativa
#### HouseStyle: Cualitativa
#### OverallQual: Cuantitativa discreta
#### OverallCond: Cuantitativa discreta
#### YearBuilt: Cuantitativa discreta
#### YearRemodAdd: Cuantitativa discreta
#### RoofStyle: Cualitativa
#### RoofMatl: Cualitativa
#### Exterior1st: Cualitativa
#### Exterior2nd: Cualitativa
#### MasVnrType: Cualitativa
#### MasVnrArea: Cuantitativa continua
#### ExterQual: Cualitativa
#### ExterCond: Cualitativa
#### Foundation: Cualitativa
#### BsmtQual: Cualitativa
#### BsmtCond: Cualitativa
#### BsmtExposure: Cualitativa
#### BsmtFinType1: Cualitativa
#### BsmtFinSF1: Cuantitativa continua
#### BsmtFinType2: Cualitativa
#### BsmtFinSF2: Cuantitativa continua
#### BsmtUnfSF: Cuantitativa continua
#### TotalBsmtSF: Cuantitativa continua
#### Heating: Cualitativa
#### HeatingQC: Cualitativa
#### CentralAir: Cualitativa
#### Electrical: Cualitativa
#### X1stFlrSF: Cuantitativa continua
#### X2ndFlrSF: Cuantitativa continua
#### LowQualFinSF: Cuantitativa continua
#### GrLivArea: Cuantitativa continua
#### BsmtFullBath: Cuantitativa discreta
#### BsmtHalfBath: Cuantitativa discreta
#### FullBath: Cuantitativa discreta
#### HalfBath: Cuantitativa discreta
#### BedroomAbvGr: Cuantitativa discreta
#### KitchenAbvGr: Cuantitativa discreta
#### KitchenQual: Cualitativa
#### TotRmsAbvGrd: Cuantitativa discreta
#### Functional: Cualitativa
#### Fireplaces: Cuantitativa discreta
#### FireplaceQu: Cualitativa
#### GarageType: Cualitativa
#### GarageYrBlt: Cuantitativa discreta
#### GarageFinish: Cualitativa
#### GarageCars: Cuantitativa discreta
#### GarageArea: Cuantitativa continua
#### GarageQual: Cualitativa
#### GarageCond: Cualitativa
#### PavedDrive: Cualitativa
#### WoodDeckSF: Cuantitativa continua
#### OpenPorchSF: Cuantitativa continua
#### EnclosedPorch: Cuantitativa continua
#### x3SsnPorch: Cualitativa
#### ScreenPorch: Cuantitativa continua
#### PoolArea: Cuantitativa continua
#### PoolQC: Cualitativa
#### Fence: Cualitativa
#### MiscFeature: Cualitativa
#### MiscVal: Cuantitativa continua
#### MoSold: Cuantitativa discreta
#### YrSold: Cuantitativa discreta
#### SaleType: Cualitativa
#### SaleCondition: Cualitativa

## Representaci칩n gr치fica
### Continuas

```{r}
hist(x = db$LotFrontage)
hist(x = db$LotArea)
hist(x = db$MasVnrArea)
hist(x = db$BsmtFinSF1)
hist(x = db$BsmtFinSF2)
hist(x = db$BsmtUnfSF)
hist(x = db$TotalBsmtSF)
hist(x = db$X1stFlrSF)
hist(x = db$X2ndFlrSF)
hist(x = db$LowQualFinSF)
hist(x = db$GrLivArea)
hist(x = db$GarageArea)
hist(x = db$WoodDeckSF)
hist(x = db$OpenPorchSF)
hist(x = db$EnclosedPorch)
hist(x = db$ScreenPorch)
hist(x = db$PoolArea)
hist(x = db$MiscVal)
```

### Discretas

```{r}
plot(db$MSSubClass)
plot(db$OverallQual)
plot(db$OverallCond)
plot(db$YearBuilt)
plot(db$YearRemodAdd)
plot(db$BsmtFullBath)
plot(db$BsmtHalfBath)
plot(db$FullBath)
plot(db$HalfBath)
plot(db$BedroomAbvGr)
plot(db$KitchenAbvGr)
plot(db$TotRmsAbvGrd)
plot(db$Fireplaces)
plot(db$GarageYrBlt)
plot(db$GarageCars)
plot(db$MoSold)
plot(db$YrSold)
```

### Cualitativas

```{r}
barplot(t1,  main = "MSZoning")
barplot(t2,  main = "Street")
barplot(t3,  main = "Alley")
barplot(t4,  main = "LotShape")
barplot(t5,  main = "LandContour")
barplot(t6,  main = "Utilities")
barplot(t7,  main = "LotConfig")
barplot(t8,  main = "LandSlope")
barplot(t9,  main = "Neighborhood")
barplot(t10,  main = "Condition1")
barplot(t11,  main = "Condition2")
barplot(t12,  main = "BldgType")
barplot(t13,  main = "HouseStyle")
barplot(t14,  main = "RoofStyle")
barplot(t15,  main = "RoofMatl")
barplot(t16,  main = "Exterior1st")
barplot(t17,  main = "Exterior2nd")
barplot(t18,  main = "MasVnrType")
barplot(t19,  main = "ExterQual")
barplot(t20,  main = "ExterCond")
barplot(t21,  main = "Foundation")
barplot(t22,  main = "BsmtQual")
barplot(t23,  main = "BsmtCond")
barplot(t24,  main = "BsmtExposure")
barplot(t25,  main = "BsmtFinType1")
barplot(t26,  main = "BsmtFinType2")
barplot(t27,  main = "Heating")
barplot(t28,  main = "HeatingQC")
barplot(t29,  main = "CentralAir")
barplot(t30,  main = "Electrical")
barplot(t31,  main = "KitchenQual")
barplot(t32,  main = "Functional")
barplot(t33,  main = "FireplaceQu")
barplot(t34,  main = "GarageType")
barplot(t35,  main = "GarageFinish")
barplot(t36,  main = "GarageQual")
barplot(t37,  main = "GarageCond")
barplot(t38,  main = "PavedDrive")
barplot(t39,  main = "PoolQC")
barplot(t40,  main = "Fence")
barplot(t41,  main = "MiscFeature")
barplot(t42,  main = "SaleType")
barplot(t43,  main = "SaleCondition")
```
